---
title: "Quiz 2"
output:
  html_notebook: default
  quiz-2: default
---
```{r}
source('pollutionmean.R')
source('complete.R')
source('corr.R')
```
**1. What value is returned by the following call to pollutantmean()? You should round your output to 3 digits.**
```{r}
pollutantmean("specdata", "sulfate", 1:10)
```
**2. What value is returned by the following call to pollutantmean()? You should round your output to 3 digits.**
```{r}
pollutantmean("specdata", "nitrate", 70:72)
```
**3. What value is returned by the following call to pollutantmean()? You should round your output to 3 digits.**
```{r}
pollutantmean("specdata", "sulfate", 34)
```
**4. What value is returned by the following call to pollutantmean()? You should round your output to 3 digits.**
```{r}
pollutantmean("specdata", "nitrate")
```
**5. What value is printed at end of the following code?**
```{r}
cc <- complete("specdata", c(6, 10, 20, 34, 100, 200, 310))
print(cc$nobs)
```
**6. What value is printed at end of the following code?**
```{r}
cc <- complete("specdata", 54)
print(cc$nobs)
```
**7. What value is printed at end of the following code?**
```{r}
set.seed(42)
cc <- complete("specdata", 332:1)
use <- sample(332, 10)
print(cc[use, "nobs"])
```
**8. What value is printed at end of the following code?**
```{r}
cr <- corr("specdata")                
cr <- sort(cr)   
set.seed(868)                
out <- round(cr[sample(length(cr), 5)], 4)
print(out)
```
**9. What value is printed at end of the following code?**
```{r}
cr <- corr("specdata", 129)                
cr <- sort(cr)                
n <- length(cr)    
set.seed(197)                
out <- c(n, round(cr[sample(n, 5)], 4))
print(out)
```
**10. What value is printed at end of the following code?**
```{r}
cr <- corr("specdata", 2000)                
n <- length(cr)                
cr <- corr("specdata", 1000)                
cr <- sort(cr)
print(c(n, round(cr, 4)))
```
